---
title: "Dataset Overview"
format:
  pdf: default
  docx: default
params:
  selected_df: "BMT"
---

```{r}
#| include: false
library(dplyr)
library(flextable)

df <- toySurvivalApp:::select_dataset(params$selected_df)

# -- calculate summary values for report --
df_summary <- df %>%
  summarize(
    across(where(is.numeric),
           .fns = list(Mean = function(x) mean(x, na.rm = TRUE),
                       Median = function(x) median(x, na.rm = TRUE))))

df_summary_bullets <- df_summary %>%
  tidyr::pivot_longer(everything(), names_sep='_', names_to=c('variable', '.value')) %>%
  rowwise() %>%
  mutate(display_text = glue::glue("{variable} | Mean: {format(round(Mean, 2), nsmall = 2)} | Median: {format(round(Median, 2), nsmall = 2)}"))

bullet_list <- function(...) {
  cat(paste0("* ", c(...), collapse = "\n"))
  cat("\n")
}

```

## Introduction

The `r params$selected_df` dataset consists of `r nrow(df)` observations of `r ncol(df)` variables.  Data can be transformed to markdown bulleted lists:

```{r results="asis"}
#| echo: false
bullet_list(df_summary_bullets$display_text) 
```

## Dataset Summary
This is the same information reformatted as a flextable.
```{r results="asis"}
#| echo: false
df_summary %>%
  flextable() %>% 
  colformat_double() %>% 
  separate_header() %>% 
  align(align = "center", part = "all") %>%
  autofit()
```

## Distributions
We can re-use the same plotting functions in the application and the output.  Please
note, exporting ggplot can be finicky.  Please select the "Download Editable Plots" export
option for vector graphic versions.
```{r}
#| echo: false
#| message: false
#| warning: false

plot_df <- df %>%
  select(where(is.numeric)) %>%
  tidyr::pivot_longer(everything())

# walk is used to prevent the printing of the plot indices
purrr::walk(
  c("Histogram", "Box Plot", "Density"),
  function(x) print(toySurvivalApp:::make_eda_plot(plot_df, x)))

```


## Appendix: Raw Data Sample
This section demonstrates that the same formatting visible in the app can be
exported to print-ready documents.
```{r results="asis"}
#| echo: false
df %>%
  head(5) %>%
  flextable() 
```
